To Do

### 2022-08-24 Summary.Rmd
Fixing mistake on the summary results

@@

pref %>% 
group_by(cover.names) %>% 
summarise(n_rows = length(cover.names)) %>% 
rename(Land_use = cover.names) %>% 
arrange(desc(n_rows)) %>% 
mutate(Cover_names = fct_recode(as.factor(Land_use),
Discard = "Barren Land", #Very different cover type, not included  
Agricultural = "Cultivated Crops", #
Natural = "Deciduous Forest", #
Urban = "Developed, High Intensity", #Greater than 50% of cover  
Urban = "Developed, Medium Intensity", #Greater than 50% of cover  
Seminatural = "Developed, Low Intensity", #Low urban impact 
Seminatural = "Developed, Open Space", #Open areas with vegetation 
Natural = "Emergent Herbaceous Wetlands", #
Natural = "Evergreen Forest", #
Agricultural = "Hay/Pasture", #Highly managed by humans 
Natural = "Herbaceous", #See explanation below 
Natural = "Mixed Forest", #
Discard = "Open Water", #Low vegetation and land, not included 
Natural = "Shrub/Scrub", #Heath classified as natural 
Natural = "Woody Wetlands")) %>% 
kbl() %>% 
kable_styling(latex_options = "hold_position", font_size = 12)

>>>>

United States land use classification with total number of occurrences within cover type in our dataset

@@

pref %>% 
group_by(cover.names) %>% 
summarise(n_rows = length(cover.names)) %>% 
rename(Land_use = cover.names) %>% 
arrange(desc(n_rows)) %>% 
mutate(Cover_names = fct_recode(as.factor(Land_use),
Discard = "Barren Land", #Very different cover type, not included  
Agricultural = "Cultivated Crops", #
Natural = "Deciduous Forest", #
Urban = "Developed, High Intensity", #Greater than 50% of cover  
Urban = "Developed, Medium Intensity", #Greater than 50% of cover  
Seminatural = "Developed, Low Intensity", #Low urban impact 
Seminatural = "Developed, Open Space", #Open areas with vegetation 
Natural = "Emergent Herbaceous Wetlands", #
Natural = "Evergreen Forest", #
Agricultural = "Hay/Pasture", #Highly managed by humans 
Natural = "Herbaceous", #See explanation below 
Natural = "Mixed Forest", #
Discard = "Open Water", #Low vegetation and land, not included 
Natural = "Shrub/Scrub", #Heath classified as natural 
Natural = "Woody Wetlands")) %>% 
kbl() %>% 
kable_styling(latex_options = "hold_position", font_size = 10)
